Twisted 11-dimensional supergravity, I

### 2021-08-09 draft.tex
suca

>>>>

Choose a splitting 
\[
\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR
\]
and denote coordinates $z_i, i=1,2,3$ and $w_a, a=1,2$.

\begin{prop}
The $Q$-twist of the 6d $\cN=(2,0)$ superconformal algebra is $\lie{osp}(6|1)$. 
\end{prop}

\begin{itemize}
\item
The even part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
\[
\lie{sl}(4) \oplus \lie{sl}(2)
\]
which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.

\item
The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ is mapped to the translations 
\[
\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) , \quad i=1,2,3.
\]

\item
The bosonic subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ is mapped to the 
rotations
\[
a_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5) , \quad (a_{ij}) \in \lie{sl}(3) .
\]

\item
The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
\[
\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5)  .
\]

\item 
The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
\[
z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) .
\]

\item 
The bosonic summand $\lie{sl}(2)$ is mapped to the triple
\[
w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5).
\]
\end{itemize}

The odd part of $\lie{osp}(6|1)$ is 
\[
\wedge^2 \CC^4 \otimes \CC^2 
\]
which we can write as $\wedge^2 W \otimes R$. 
Let us further split $W = L \oplus \CC$, with $L = \CC^3$ the fundamental $\lie{sl}(3)$ representation. 
Then the odd part decomposes as
\[
\wedge L \otimes R \oplus \wedge^2 L \otimes R .
\]

\begin{itemize} 
\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
It is mapped to the fields 
\[
z_i \d w_a \in \Omega^{1,0}(\CC^3) .
\] 
\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
It is mapped to the fields
\[
\ep_{ij} z_i w_a \d z_j \in \Omega^{1,0}(\CC^3) , \quad a = 1,2, \quad i,j = 1,2,3. 
\]
\end{itemize}
